Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-04-15 Scripts/Initial_Analysis.Rmd
Included reporting to fix specief species errors

  print(Spp)

@@

@@

spp_list <- c(600004,
              600005,
              600245#,
              # 600006
              )

>>>>

  #### Control for Spp id so I can fix problems

if(file.exists("~/Desktop/spp_df.csv") == FALSE){
  spp_df <- tibble() %>% 
    write_csv(.,
            "~/Desktop/spp_df.csv")
}

  suppressMessages(
    spp_df <- read_csv("~/Desktop/spp_df.csv")
  )
  spp_df <- tibble(Spp) %>% 
    bind_rows(spp_df) %>% 
    write_csv(.,
              "~/Desktop/spp_df.csv")

@@

spp_list <- unique(Transboundary_spp$taxon_key)

@@

spp_list <- c(600004,
              600005,
              600245,
              600006
              )
